---
title: "SL_SNA_correlations_ANOVA_regressions"
author: "Drew Walker"
date: "10/3/2021"
output: html_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stargazer)
library(table1)
library(ggpubr)
library("Hmisc")
library(psych)

```

# Model details:

## Outcomes :

-   Network Size (network_size)

    -   Network size can be depend on situation and type of relationship, but overall strong evidence for larger network size predicting higher perceived support and relationship satisfaction

        -   Higher network size associated with higher perceived support in study with type 1 diabetes patients [@cheyne2021]

-   Repeated Vol Visits (avg_alter_freq)

    -   "Granovetter's 'strength of weak ties' argument concludes that weak ties provide better connections to different social mileus because they connect socially dissimilar people. Greater range within a network (size and heterogeneity, lower density), more access to diverse sources of support, and greater availability of support

    -   Closeness of relationships persisted in its association with support perceptions and satisfaction. [@vaux1985]

-   Network Density (density)

    -   Research on density is mixed, though research has indicated differential benefits of high and low density under different conditions-- high density networks may help best "in situations where retrenchnment, recuperation, and validation is the appropriate response." . "Low-density networks may work best in facilitating change and adaptation to new situations." [@vaux1985]

        -   Study for personal support networks for patients with chronic pain found higher density predictive of higher support satisfaction. Also, Diversity of ties in network is often associated with higher perceived support and relationship satisfaction [@fernández-peña2020]

        -   Evidence from a recent integrated review suggested that higher density among actors may allow for better mobilization of support during times of crisis [@frança2018]

-   Total SL Visits (total_visits)

-   Diversity score

    -   Shannon entropy: represents diversity of alter score

    -   Diversity of ties in network is often associated with higher perceived support and relationship satisfaction [@fernández-peña2020][@wellman2018]

## Predictors

-   Age (age)
-   Length of stay (total_los)
-   Total number of admissions (total_admissions)
-   Network density (density)
-   Deceased (deceased), if patient passed after study recruitment
-   Designated Palliative Patient Status (dpp): status indicated by Streetlight program for patients in major disease populations (not other) patients who have been admitted 3x or more, or patients who are followed by pal care team
-   Project Team
-   Gender

## Covariates for adjusted models

-   After finding significance for most models incoprorating total LOS and Hospital admissions for outcomes, we ran additional models adjusting for total length of stay and hospital admissions

# EDA

## outcome distributions

```{r, describe_vars}
describe(sna_ego_list_for_model)

outcomes <- sna_ego_list_for_model %>% 
  select(network_size,avg_alter_freq,total_visits,density)
outcomes_plot <- hist.data.frame(outcomes, na.big = TRUE)

hist(outcomes$density,breaks=10)
```

```{r, predictor_plots}
predictors <- sna_ego_list_for_model %>% 
  select(age,gender,deceased,dpp,project_team,days_in_SL,total_admissions,total_los)
predictor_plot <- hist.data.frame(predictors)

predictors_log <- predictors %>% 
  mutate(log_total_los = log(total_los),
         log_days_in_SL = log(days_in_SL),
         log_total_admissions = log(total_ad))

hist.data.frame(predictors_log)



hist(predictors_log$log_total_los)

# 1 age missing
# 1 female category
# change none 
```

```{r,data_prep}
#read data 
sna_ego_list_for_model <- read_csv("sna_ego_list.csv")
#factors 
factor_vars <- c("deceased", "dpp", "project_team", "gender")
sna_ego_list_for_model<- sna_ego_list_for_model %>% 
       mutate_each_(funs(factor(.)),factor_vars) %>% 
  mutate(log_total_los = log(total_los),#predictors
         log_days_in_SL = log(days_in_SL),
         log_total_admissions = log(total_admissions),
         log_network_size = log(network_size),
         log_avg_alter_freq = log(avg_alter_freq),
         log_total_visits = log(total_visits),
         log_density= log(density))


str(sna_ego_list_for_model)
#age as number
sna_ego_list_for_model$age <- as.numeric(sna_ego_list_for_model$age)
```

# Crude linear models for outcome network size

```{r,network_size_models}
#Crude models
#Network_size_models
network_size_age_crude <- lm(network_size ~ age, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(network_size_age_crude)
confint(network_size_age_crude)

#LOS
network_size_los_crude <- lm(network_size ~ total_los, data =sna_ego_list_for_model)  
summary(network_size_los_crude)
confint(network_size_los_crude)

#total hospital admissions
network_size_admissions_crude <- lm(network_size ~ total_admissions, data =sna_ego_list_for_model)  
summary(network_size_admissions_crude)
confint(network_size_admissions_crude)

#network size density 
network_size_density_crude <- lm(network_size ~ density, data =sna_ego_list_for_model)  
summary(network_size_density_crude)
confint(network_size_density_crude)

#density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
network_size_deceased_crude <- lm(network_size ~ deceased, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(network_size_deceased_crude)
confint(network_size_deceased_crude)
#dpp
network_size_dpp_crude <- lm(network_size ~ dpp, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(network_size_dpp_crude)
confint(network_size_dpp_crude)

#project_team
network_size_project_team_crude <- lm(network_size ~ project_team, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(network_size_project_team_crude)

confint(network_size_project_team_crude)

#gender
network_size_gender_crude <- lm(network_size ~ gender, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(network_size_gender_crude)
confint(network_size_gender_crude)
#both predict? that doesn't make sense...
```

# Adjusted network size models

```{r,network_size_adjusted}
####ADJUSTED MODELS#### 
#Network_size_models
network_size_age_adjusted <- lm(network_size ~ age + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(network_size_age_adjusted)
confint(network_size_age_adjusted)

#LOS
network_size_los_adjusted <- lm(network_size ~ total_los  + total_admissions, data =sna_ego_list_for_model)  
summary(network_size_los_adjusted)
confint(network_size_los_adjusted)

#network size density 
network_size_density_adjusted <- lm(network_size ~ density + total_los + total_admissions, data =sna_ego_list_for_model)  
summary(network_size_density_adjusted)
confint(network_size_density_adjusted)

#density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
network_size_deceased_adjusted <- lm(network_size ~ deceased + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(network_size_deceased_adjusted)
confint(network_size_deceased_adjusted)
#dpp
network_size_dpp_adjusted <- lm(network_size ~ dpp + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(network_size_dpp_adjusted)
confint(network_size_dpp_adjusted)

#project_team
network_size_project_team_adjusted <- lm(network_size ~ project_team + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(network_size_project_team_adjusted)
confint(network_size_project_team_adjusted)

#gender
network_size_gender_adjusted <- lm(network_size ~ gender + total_los  + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(network_size_gender_adjusted)
confint(network_size_gender_adjusted)
#both predict? that doesn't make sense...
```

# Crude linear models for outcome repeat visits

```{r, llm for repeated visits}
#Crude models
#avg_alter_freq_models
avg_alter_freq_age_crude <- lm(avg_alter_freq ~ age, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(avg_alter_freq_age_crude)
confint(avg_alter_freq_age_crude)

#LOS
avg_alter_freq_total_los_crude <- lm(avg_alter_freq ~ total_los, data =sna_ego_list_for_model)  
summary(avg_alter_freq_total_los_crude)
confint(avg_alter_freq_total_los_crude)

#admissions
avg_alter_freq_admissions_crude <- lm(avg_alter_freq ~ total_admissions, data =sna_ego_list_for_model)  
summary(avg_alter_freq_admissions_crude)
confint(avg_alter_freq_admissions_crude)
#network size density 
avg_alter_freq_density_crude <- lm(avg_alter_freq ~ density, data =sna_ego_list_for_model)  
summary(avg_alter_freq_density_crude)
confint(avg_alter_freq_density_crude)

#density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
avg_alter_freq_deceased_crude <- lm(avg_alter_freq ~ deceased, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(avg_alter_freq_deceased_crude)
confint(avg_alter_freq_deceased_crude)
#dpp
avg_alter_freq_dpp_crude <- lm(avg_alter_freq ~ dpp, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(avg_alter_freq_dpp_crude)
confint(avg_alter_freq_dpp_crude)

#project_team
avg_alter_freq_project_team_crude <- lm(avg_alter_freq ~ project_team, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(avg_alter_freq_project_team_crude)

confint(avg_alter_freq_project_team_crude)

#gender
avg_alter_freq_gender_crude <- lm(avg_alter_freq ~ gender, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(avg_alter_freq_gender_crude)
confint(avg_alter_freq_gender_crude)
#both predict? that doesn't make sense...
```

# Adjusted alter frequency models

```{r,alter_freq_adjusted}
#### ADJUSTED MODELS ######
#avg_alter_freq_models
avg_alter_freq_age_adjusted <- lm(avg_alter_freq ~ age + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(avg_alter_freq_age_adjusted)
confint(avg_alter_freq_age_adjusted)

#LOS and admissions
avg_alter_freq_los_adjusted <- lm(avg_alter_freq ~ total_los  + total_admissions, data =sna_ego_list_for_model)  
summary(avg_alter_freq_los_adjusted)
confint(avg_alter_freq_los_adjusted)

#network size density 
avg_alter_freq_density_adjusted <- lm(avg_alter_freq ~ density + total_los + total_admissions, data =sna_ego_list_for_model)  
summary(avg_alter_freq_density_adjusted)
confint(avg_alter_freq_density_adjusted)

#density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
avg_alter_freq_deceased_adjusted <- lm(avg_alter_freq ~ deceased + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(avg_alter_freq_deceased_adjusted)
confint(avg_alter_freq_deceased_adjusted)
#dpp
avg_alter_freq_dpp_adjusted <- lm(avg_alter_freq ~ dpp + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(avg_alter_freq_dpp_adjusted)
confint(avg_alter_freq_dpp_adjusted)

#project_team
avg_alter_freq_project_team_adjusted <- lm(avg_alter_freq ~ project_team + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(avg_alter_freq_project_team_adjusted)
confint(avg_alter_freq_project_team_adjusted)

#gender
avg_alter_freq_gender_adjusted <- lm(avg_alter_freq ~ gender + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(avg_alter_freq_gender_adjusted)
confint(avg_alter_freq_gender_adjusted)
#both predict? that doesn't make sense...

```

# Crude linear models for outcome network density

```{r, lm_on_density}
#Crude models
#density_models
density_age_crude <- lm(density ~ age, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(density_age_crude)
confint(density_age_crude)

#LOS
density_total_los_crude <- lm(density ~ total_los, data =sna_ego_list_for_model)  
summary(density_total_los_crude)
confint(density_total_los_crude)

#admissions
density_admissions_crude <- lm(density ~ total_admissions, data =sna_ego_list_for_model)  
summary(density_admissions_crude)
confint(density_admissions_crude)


#density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
density_deceased_crude <- lm(density ~ deceased, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(density_deceased_crude)
confint(density_deceased_crude)
#dpp
density_dpp_crude <- lm(density ~ dpp, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(density_dpp_crude)
confint(density_dpp_crude)

#project_team
density_project_team_crude <- lm(density ~ project_team, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(density_project_team_crude)

confint(density_project_team_crude)

# Density



#gender
density_gender_crude <- lm(density ~ gender, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(density_gender_crude)
confint(density_gender_crude)
#both predict? that doesn't make sense...

```

# Adjusted network density models

```{r,density_adjusted}
#### ADJUSTED MODELS ######
#density_models
density_age_adjusted <- lm(density ~ age + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(density_age_adjusted)
confint(density_age_adjusted)

#LOS and admissions
density_los_adjusted <- lm(density ~ total_los  + total_admissions, data =sna_ego_list_for_model)  
summary(density_los_adjusted)
confint(density_los_adjusted)

# It will necessarily become more sparse as number of connections increases

#deceased
density_deceased_adjusted <- lm(density ~ deceased + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(density_deceased_adjusted)
confint(density_deceased_adjusted)
#dpp
density_dpp_adjusted <- lm(density ~ dpp + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(density_dpp_adjusted)
confint(density_dpp_adjusted)

#project_team
density_project_team_adjusted <- lm(density ~ project_team + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(density_project_team_adjusted)
confint(density_project_team_adjusted)

#gender
density_gender_adjusted <- lm(density ~ gender + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(density_gender_adjusted)
confint(density_gender_adjusted)
#both predict? that doesn't make sense...

#density_models adjusted for network size
density_network_size_crude <- lm(density ~ network_size, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(density_network_size_crude)
confint(density_network_size_crude)

alt_tie_freq_density <- lm(avg_alter_freq ~ density + network_size + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th


summary(alt_tie_freq_density)
confint(alt_tie_freq_density)

```

# Crude linear models for outcome Total SL Visits

```{r, lm_on_total_visits}
#Crude models
#total_visits_models
total_visits_age_crude <- lm(total_visits ~ age, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(total_visits_age_crude)
confint(total_visits_age_crude)

#LOS
total_visits_total_los_crude <- lm(total_visits ~ total_los, data =sna_ego_list_for_model)  
summary(total_visits_total_los_crude)
confint(total_visits_total_los_crude)

#admissions
total_visits_admissions_crude <- lm(total_visits ~ total_admissions, data =sna_ego_list_for_model)  
summary(total_visits_admissions_crude)
confint(total_visits_admissions_crude)

#total_visits super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
total_visits_deceased_crude <- lm(total_visits ~ deceased, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(total_visits_deceased_crude)
confint(total_visits_deceased_crude)
#dpp
total_visits_dpp_crude <- lm(total_visits ~ dpp, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(total_visits_dpp_crude)
confint(total_visits_dpp_crude)

#project_team
total_visits_project_team_crude <- lm(total_visits ~ project_team, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(total_visits_project_team_crude)

confint(total_visits_project_team_crude)

#gender
total_visits_gender_crude <- lm(total_visits ~ gender, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(total_visits_gender_crude)
confint(total_visits_gender_crude)
#both predict? that doesn't make sense...


```

# Adjusted total SL visit models

```{r,total_sl_adjusted}
#### ADJUSTED MODELS ######
#total_visits_models
total_visits_age_adjusted <- lm(total_visits ~ age + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of total admissions and los

summary(total_visits_age_adjusted)
confint(total_visits_age_adjusted)

#LOS and admissions
total_visits_los_adjusted <- lm(total_visits ~ total_los  + total_admissions, data =sna_ego_list_for_model)  
summary(total_visits_los_adjusted)
confint(total_visits_los_adjusted)


#deceased
total_visits_deceased_adjusted <- lm(total_visits ~ deceased + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(total_visits_deceased_adjusted)
confint(total_visits_deceased_adjusted)
#dpp
total_visits_dpp_adjusted <- lm(total_visits ~ dpp + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(total_visits_dpp_adjusted)
confint(total_visits_dpp_adjusted)

#project_team
total_visits_project_team_adjusted <- lm(total_visits ~ project_team + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(total_visits_project_team_adjusted)
confint(total_visits_project_team_adjusted)

#gender
total_visits_gender_adjusted <- lm(total_visits ~ gender + total_los + total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(total_visits_gender_adjusted)
confint(total_visits_gender_adjusted)
#both predict? that doesn't make sense...

```

# Literature on network characteristics and social support

Networks of small size, strong ties, high density, high homogeneity, and
low dispersion appear to be helpful in maintaining social identity and
hence health and well-being outcomes when these are promoted by
maintenance of the networks. However, change in social roles and
identities, and hence health and well-being during such change, is
facilitated by larger networks with weaker ties, lower density, and
greater social and cultural heterogeneity [26], [27], [40], [48]--[49][50][51]. [@hemmati2014]

# Discussion points

-   multiplexity of visit type

    -   Need to also measure SGL:

        -   Haythornthwaite ([2005](https://www.tandfonline.com/doi/full/10.1080/10410236.2016.1242032?casa_token=Cs3Ug6AgxgwAAAAA%3AywV4WhQjG-17SbYUy52F1_2-aVznMi-1iPm1qdBWers3M58EosaXMZdTOCpZvUPbt4z3zyda1E-i#)) suggested that communication multiplexity is associated with relational strength. Ledbetter ([2009](https://www.tandfonline.com/doi/full/10.1080/10410236.2016.1242032?casa_token=Cs3Ug6AgxgwAAAAA%3AywV4WhQjG-17SbYUy52F1_2-aVznMi-1iPm1qdBWers3M58EosaXMZdTOCpZvUPbt4z3zyda1E-i#))
            examined the detailed patterns of multiplexity and found that media use
            patterns predicted friendship interdependence. Vergeer and Pelzer ([2009](https://www.tandfonline.com/doi/full/10.1080/10410236.2016.1242032?casa_token=Cs3Ug6AgxgwAAAAA%3AywV4WhQjG-17SbYUy52F1_2-aVznMi-1iPm1qdBWers3M58EosaXMZdTOCpZvUPbt4z3zyda1E-i#))
            showed that offline network capital---measured by communication
            face-to-face or on the phone---was associated with higher social support
            and lower loneliness, while online network capital---measured by
            communication via e-mail, chat, or instant messaging---did not show these
            benefits.
