---
title: "SL_SNA_log_regressions"
author: "Drew Walker"
date: "10/3/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stargazer)
library(table1)
library(ggpubr)
library("Hmisc")
library(psych)

```



```{r,data_prep}
#read data 
sna_ego_list_for_model <- read_csv("sna_ego_list.csv")
#factors 
factor_vars <- c("deceased", "dpp", "project_team", "gender")
sna_ego_list_for_model<- sna_ego_list_for_model %>% 
       mutate_each_(funs(factor(.)),factor_vars) %>% 
  mutate(log_total_los = log(total_los),#predictors
         log_days_in_SL = log(days_in_SL),
         log_total_admissions = log(total_admissions),
         log_network_size = log(network_size),
         log_avg_alter_freq = log(avg_alter_freq),
         log_total_visits = log(total_visits),
         log_density= log(density))
sna_ego_list_for_model <- within(sna_ego_list_for_model, project_team <- relevel(project_team, ref = "None"))

#age as number
sna_ego_list_for_model$age <- as.numeric(sna_ego_list_for_model$age)
```
# Model details:
## Outcomes :  
* Network Size (network_size)
* * Log network size (log_network_size)
* Repeated Vol Visits (avg_alter_freq)
* * Log avg_alter_freq = log_avg_alter_freq
* Network Density (density)
* * log_density
* Total SL Visits (total_visits)
* * log_total_visits
* Entropy (network alter diversity of closeness)-- shannons entropy of volunteer repeat visits-- showing diversity of support sources (weak and strong ties offer advantages for different situations, good to have mix in network. Higher score=greater mix. Log transformed already, so not doing it twice!)

## Predictors
* Age (age)
* Length of stay (total_los)
* * log_total_los
* Total number of admissions (total_admissions)
* * log_total_admissions
* Network density (density)
* * log_density
* Deceased (deceased), if patient passed after study recruitment
* Designated Palliative Patient Status (dpp): status indicated by Streetlight program for patients in major disease populations (not other) patients who have been admitted 3x or more, or patients who are followed by pal care team
* network alter diversity
* Project Team
* Gender


## Covariates for adjusted models
* After finding significance for most models incoprorating total LOS and Hospital admissions for outcomes, we ran additional models adjusting for total length of stay and hospital admissions

# EDA 

## outcome distributions
```{r, describe_vars}
outcomes <- sna_ego_list_for_model %>% 
  select(network_size,avg_alter_freq,total_visits,density,entropy)
outcomes_plot <- hist.data.frame(outcomes, na.big = TRUE)

outcomes_log<- sna_ego_list_for_model %>% 
  select(network_size,
         avg_alter_freq,
         total_visits,
         density,
         entropy)
```

```{r, predictor_plots}
predictors <- sna_ego_list_for_model %>% 
  select(age,gender,deceased,dpp,project_team,days_in_SL,total_admissions,total_los)
predictor_plot <- hist.data.frame(predictors)

predictors_log <- predictors %>% 
  mutate(log_total_los = log(total_los),
         log_days_in_SL = log(days_in_SL),
         log_total_admissions = log(total_admissions))

hist.data.frame(predictors_log)



hist(predictors_log$log_total_los)

# 1 age missing
# 1 female category
# change none 
```
# Crude linear models for outcome log network size
```{r,log_network_size_models}
#Crude models
#log_network_size_models
log_network_size_age_crude <- lm(log_network_size ~ age, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(log_network_size_age_crude)
confint(log_network_size_age_crude)

#LOS
log_network_size_los_crude <- lm(log_network_size ~ log_total_los, data =sna_ego_list_for_model)  
summary(log_network_size_los_crude)
confint(log_network_size_los_crude)

#total hospital admissions
log_network_size_admissions_crude <- lm(log_network_size ~ log_total_admissions, data =sna_ego_list_for_model)  
summary(log_network_size_admissions_crude)
confint(log_network_size_admissions_crude)

#log_density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
log_network_size_deceased_crude <- lm(log_network_size ~ deceased, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_network_size_deceased_crude)
confint(log_network_size_deceased_crude)
#dpp
log_network_size_dpp_crude <- lm(log_network_size ~ dpp, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_network_size_dpp_crude)
confint(log_network_size_dpp_crude)

#project_team
log_network_size_project_team_crude <- lm(log_network_size ~ project_team, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_network_size_project_team_crude)

confint(log_network_size_project_team_crude)

#gender
log_network_size_gender_crude <- lm(log_network_size ~ gender, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_network_size_gender_crude)
confint(log_network_size_gender_crude)
#both predict? that doesn't make sense...
```
# Adjusted network size models
```{r,log_network_size_adjusted}
####ADJUSTED MODELS#### 
#log_network_size_models
log_network_size_age_adjusted <- lm(log_network_size ~ age + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(log_network_size_age_adjusted)
confint(log_network_size_age_adjusted)

#LOS
log_network_size_los_adjusted <- lm(log_network_size ~ log_total_los  + log_total_admissions, data =sna_ego_list_for_model)  
summary(log_network_size_los_adjusted)
confint(log_network_size_los_adjusted)

#admissions
log_network_size_admissions_adjusted <- lm(log_network_size ~ log_total_admissions + log_total_los, data =sna_ego_list_for_model)  
summary(log_network_size_admissions_adjusted)
confint(log_network_size_admissions_adjusted)

#network size log_density 

#log_density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
log_network_size_deceased_adjusted <- lm(log_network_size ~ deceased + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_network_size_deceased_adjusted)
confint(log_network_size_deceased_adjusted)
#dpp
log_network_size_dpp_adjusted <- lm(log_network_size ~ dpp + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_network_size_dpp_adjusted)
confint(log_network_size_dpp_adjusted)

#project_team
log_network_size_project_team_adjusted <- lm(log_network_size ~ project_team + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_network_size_project_team_adjusted)
confint(log_network_size_project_team_adjusted)

#gender
log_network_size_gender_adjusted <- lm(log_network_size ~ gender + log_total_los  + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_network_size_gender_adjusted)
confint(log_network_size_gender_adjusted)
#both predict? that doesn't make sense...
```

# Crude linear models for outcome repeat visits
```{r, llm for repeated visits}
#Crude models
#log_avg_alter_freq_models
log_avg_alter_freq_age_crude <- lm(log_avg_alter_freq ~ age, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(log_avg_alter_freq_age_crude)
confint(log_avg_alter_freq_age_crude)

#LOS
log_avg_alter_freq_log_total_los_crude <- lm(log_avg_alter_freq ~ log_total_los, data =sna_ego_list_for_model)  
summary(log_avg_alter_freq_log_total_los_crude)
confint(log_avg_alter_freq_log_total_los_crude)

#admissions
log_avg_alter_freq_admissions_crude <- lm(log_avg_alter_freq ~ log_total_admissions, data =sna_ego_list_for_model)  
summary(log_avg_alter_freq_admissions_crude)
confint(log_avg_alter_freq_admissions_crude)
#network size log_density 

log_avg_alter_freq_log_density_crude <- lm(log_avg_alter_freq ~ log_density, data =subset(sna_ego_list_for_model,density>0))

summary(log_avg_alter_freq_log_density_crude)
confint(log_avg_alter_freq_log_density_crude)

#log_density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
log_avg_alter_freq_deceased_crude <- lm(log_avg_alter_freq ~ deceased, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_avg_alter_freq_deceased_crude)
confint(log_avg_alter_freq_deceased_crude)
#dpp
log_avg_alter_freq_dpp_crude <- lm(log_avg_alter_freq ~ dpp, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_avg_alter_freq_dpp_crude)
confint(log_avg_alter_freq_dpp_crude)

#project_team
log_avg_alter_freq_project_team_crude <- lm(log_avg_alter_freq ~ project_team, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_avg_alter_freq_project_team_crude)

confint(log_avg_alter_freq_project_team_crude)

#gender
log_avg_alter_freq_gender_crude <- lm(log_avg_alter_freq ~ gender, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_avg_alter_freq_gender_crude)
confint(log_avg_alter_freq_gender_crude)
#both predict? that doesn't make sense...
```
# Adjusted alter frequency models
```{r,alter_freq_adjusted} 
#### ADJUSTED MODELS ######
#log_avg_alter_freq_models
log_avg_alter_freq_age_adjusted <- lm(log_avg_alter_freq ~ age + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(log_avg_alter_freq_age_adjusted)
confint(log_avg_alter_freq_age_adjusted)

#LOS and admissions
log_avg_alter_freq_los_adjusted <- lm(log_avg_alter_freq ~ log_total_los  + log_total_admissions, data =sna_ego_list_for_model)  
summary(log_avg_alter_freq_los_adjusted)
confint(log_avg_alter_freq_los_adjusted)



#log_density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
log_avg_alter_freq_deceased_adjusted <- lm(log_avg_alter_freq ~ deceased + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_avg_alter_freq_deceased_adjusted)
confint(log_avg_alter_freq_deceased_adjusted)
#dpp
log_avg_alter_freq_dpp_adjusted <- lm(log_avg_alter_freq ~ dpp + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_avg_alter_freq_dpp_adjusted)
confint(log_avg_alter_freq_dpp_adjusted)

#project_team
log_avg_alter_freq_project_team_adjusted <- lm(log_avg_alter_freq ~ project_team + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_avg_alter_freq_project_team_adjusted)
confint(log_avg_alter_freq_project_team_adjusted)

#gender
log_avg_alter_freq_gender_adjusted <- lm(log_avg_alter_freq ~ gender + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_avg_alter_freq_gender_adjusted)
confint(log_avg_alter_freq_gender_adjusted)
#both predict? that doesn't make sense...
#alter freq and  log_density 
log_avg_alter_freq_log_density_adjusted <- lm(log_avg_alter_freq ~ log_density + log_total_los + log_total_admissions, data =subset(sna_ego_list_for_model,density>0))
summary(log_avg_alter_freq_log_density_adjusted)
confint(log_avg_alter_freq_log_density_adjusted)
#alter freq and log density, and log network size
log_avg_alter_freq_log_density_and_network_size_adjusted <- lm(log_avg_alter_freq ~ log_density + log_network_size + log_total_los + log_total_admissions, data =subset(sna_ego_list_for_model,density>0))    #This model adds in the covariate effect of th


summary(log_avg_alter_freq_log_density_and_network_size_adjusted)
confint(log_avg_alter_freq_log_density_and_network_size_adjusted)

```
# Crude linear models for outcome network log_density

```{r, lm_on_log_density}
#Crude models
#log_density_models
log_density_age_crude <- lm(log_density ~ age, data =subset(sna_ego_list_for_model,density>0))    #This model adds in the covariate effect of th

summary(log_density_age_crude)
confint(log_density_age_crude)

#LOS
log_density_log_total_los_crude <- lm(log_density ~ log_total_los, data =subset(sna_ego_list_for_model,density>0))
summary(log_density_log_total_los_crude)
confint(log_density_log_total_los_crude)

#admissions
log_density_admissions_crude <- lm(log_density ~ log_total_admissions, data =subset(sna_ego_list_for_model,density>0))
summary(log_density_admissions_crude)
confint(log_density_admissions_crude)


#log_density super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
log_density_deceased_crude <- lm(log_density ~ deceased, data= subset(sna_ego_list_for_model,density>0))    #This model adds in the covariate effect of th
summary(log_density_deceased_crude)
confint(log_density_deceased_crude)
#dpp
log_density_dpp_crude <- lm(log_density ~ dpp, data =subset(sna_ego_list_for_model,density>0))   #This model adds in the covariate effect of th
summary(log_density_dpp_crude)
confint(log_density_dpp_crude)

#project_team
log_density_project_team_crude <- lm(log_density ~ project_team, data =subset(sna_ego_list_for_model,density>0))#This model adds in the covariate effect of th

summary(log_density_project_team_crude)

confint(log_density_project_team_crude)

# log_density



#gender
log_density_gender_crude <- lm(log_density ~ gender, data =subset(sna_ego_list_for_model,density>0))    #This model adds in the covariate effect of th
summary(log_density_gender_crude)
confint(log_density_gender_crude)
#both predict? that doesn't make sense...

```
# Adjusted network log_density models
```{r,log_density_adjusted} 
#### ADJUSTED MODELS ######
#log_density_models
log_density_age_adjusted <- lm(log_density ~ age + log_total_los + log_total_admissions, data =subset(sna_ego_list_for_model,density>0))   #This model adds in the covariate effect of th

summary(log_density_age_adjusted)
confint(log_density_age_adjusted)

#LOS and admissions
log_density_los_adjusted <- lm(log_density ~ log_total_los  + log_total_admissions, data =subset(sna_ego_list_for_model,density>0)) 
summary(log_density_los_adjusted)
confint(log_density_los_adjusted)

# It will necessarily become more sparse as number of connections increases

#deceased
log_density_deceased_adjusted <- lm(log_density ~ deceased + log_total_los + log_total_admissions, data =subset(sna_ego_list_for_model,density>0))    #This model adds in the covariate effect of th
summary(log_density_deceased_adjusted)
confint(log_density_deceased_adjusted)
#dpp
log_density_dpp_adjusted <- lm(log_density ~ dpp + log_total_los + log_total_admissions, data =subset(sna_ego_list_for_model,density>0))   #This model adds in the covariate effect of th
summary(log_density_dpp_adjusted)
confint(log_density_dpp_adjusted)

#project_team
log_density_project_team_adjusted <- lm(log_density ~ project_team + log_total_los + log_total_admissions, data =subset(sna_ego_list_for_model,density>0))   #This model adds in the covariate effect of th
summary(log_density_project_team_adjusted)
confint(log_density_project_team_adjusted)

#gender
log_density_gender_adjusted <- lm(log_density ~ gender + log_total_los + log_total_admissions, data =subset(sna_ego_list_for_model,density>0))    #This model adds in the covariate effect of th
summary(log_density_gender_adjusted)
confint(log_density_gender_adjusted)
#both predict? that doesn't make sense...

#log_density_models adjusted for network size
log_density_log_network_size_crude <- lm(log_density ~ log_network_size, data =subset(sna_ego_list_for_model,density>0))    #This model adds in the covariate effect of th

summary(log_density_log_network_size_crude)
confint(log_density_log_network_size_crude)



```
# Crude linear models for outcome Total SL Visits

```{r, lm_on_log_total_visits}
#Crude models
#log_total_visits_models
log_total_visits_age_crude <- lm(log_total_visits ~ age, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(log_total_visits_age_crude)
confint(log_total_visits_age_crude)

#LOS
log_total_visits_log_total_los_crude <- lm(log_total_visits ~ log_total_los, data =sna_ego_list_for_model)  
summary(log_total_visits_log_total_los_crude)
confint(log_total_visits_log_total_los_crude)

#admissions
log_total_visits_admissions_crude <- lm(log_total_visits ~ log_total_admissions, data =sna_ego_list_for_model)  
summary(log_total_visits_admissions_crude)
confint(log_total_visits_admissions_crude)

#log_total_visits super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
log_total_visits_deceased_crude <- lm(log_total_visits ~ deceased, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_deceased_crude)
confint(log_total_visits_deceased_crude)
#dpp
log_total_visits_dpp_crude <- lm(log_total_visits ~ dpp, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_dpp_crude)
confint(log_total_visits_dpp_crude)

#project_team
log_total_visits_project_team_crude <- lm(log_total_visits ~ project_team, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_project_team_crude)

confint(log_total_visits_project_team_crude)

#gender
log_total_visits_gender_crude <- lm(log_total_visits ~ gender, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_gender_crude)
confint(log_total_visits_gender_crude)
#both predict? that doesn't make sense...



```
# Adjusted total SL visit models
```{r,total_sl_visit_adjusted} 
#### ADJUSTED MODELS ######
#log_total_visits_models
log_total_visits_age_adjusted <- lm(log_total_visits ~ age + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of total admissions and los

summary(log_total_visits_age_adjusted)
confint(log_total_visits_age_adjusted)

#LOS and admissions
log_total_visits_los_adjusted <- lm(log_total_visits ~ log_total_los  + log_total_admissions, data =sna_ego_list_for_model)  
summary(log_total_visits_los_adjusted)
confint(log_total_visits_los_adjusted)


#deceased
log_total_visits_deceased_adjusted <- lm(log_total_visits ~ deceased + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_deceased_adjusted)
confint(log_total_visits_deceased_adjusted)
#dpp
log_total_visits_dpp_adjusted <- lm(log_total_visits ~ dpp + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_dpp_adjusted)
confint(log_total_visits_dpp_adjusted)

#project_team
log_total_visits_project_team_adjusted <- lm(log_total_visits ~ project_team + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_project_team_adjusted)
confint(log_total_visits_project_team_adjusted)

#gender
log_total_visits_gender_adjusted <- lm(log_total_visits ~ gender + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_gender_adjusted)
confint(log_total_visits_gender_adjusted)
#log density
# This may be tied to the fact that each visit is a chance for a tie to be made, so more visits = higher denominator of volunteers + also higher chance at co-visits so unsure what to make
log_total_visits_log_density_adjusted <- lm(log_total_visits ~ log_density + log_total_los + log_total_admissions, data =subset(sna_ego_list_for_model,density>0))
summary(log_total_visits_log_density_adjusted)
confint(log_total_visits_log_density_adjusted)

```

```{r, lm_on_log_total_visits_crude}
#Crude models
#log_total_visits_models
log_total_visits_age_crude <- lm(log_total_visits ~ age, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th

summary(log_total_visits_age_crude)
confint(log_total_visits_age_crude)

#LOS
log_total_visits_log_total_los_crude <- lm(log_total_visits ~ log_total_los, data =sna_ego_list_for_model)  
summary(log_total_visits_log_total_los_crude)
confint(log_total_visits_log_total_los_crude)

#admissions
log_total_visits_admissions_crude <- lm(log_total_visits ~ log_total_admissions, data =sna_ego_list_for_model)  
summary(log_total_visits_admissions_crude)
confint(log_total_visits_admissions_crude)

#log_total_visits super high predictor of network size-- may be colinearity here 
# It will necessarily become more sparse as number of connections increases

#deceased
log_total_visits_deceased_crude <- lm(log_total_visits ~ deceased, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_deceased_crude)
confint(log_total_visits_deceased_crude)
#dpp
log_total_visits_dpp_crude <- lm(log_total_visits ~ dpp, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_dpp_crude)
confint(log_total_visits_dpp_crude)

#project_team
log_total_visits_project_team_crude <- lm(log_total_visits ~ project_team, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_project_team_crude)

confint(log_total_visits_project_team_crude)

#gender
log_total_visits_gender_crude <- lm(log_total_visits ~ gender, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(log_total_visits_gender_crude)
confint(log_total_visits_gender_crude)
#both predict? that doesn't make sense...



```

#  Crude shannon entropy models
```{r,crude_entropy} 
#### ADJUSTED MODELS ######
#entropy_models
entropy_age <- lm(entropy ~ age, data =sna_ego_list_for_model)    #This model adds in the covariate effect of total admissions and los

summary(entropy_age)
confint(entropy_age)

#LOS and admissions
entropy_los_adjusted <- lm(entropy ~ log_total_los, data =sna_ego_list_for_model)  
summary(entropy_los_adjusted)
confint(entropy_los_adjusted)

entropy_log_total_admissions <- lm(entropy ~ log_total_admissions, data =sna_ego_list_for_model)  
summary(entropy_log_total_admissions)
confint(entropy_log_total_admissions)

#deceased
entropy_deceased <- lm(entropy ~ deceased, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(entropy_deceased)
confint(entropy_deceased)
#dpp
entropy_dpp <- lm(entropy ~ dpp, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(entropy_dpp)
confint(entropy_dpp)

#project_team
entropy_project_team <- lm(entropy ~ project_team, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(entropy_project_team)
confint(entropy_project_team)

#gender
entropy_gender <- lm(entropy ~ gender, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(entropy_gender)
confint(entropy_gender)
#log density
# This may be tied to the fact that each visit is a chance for a tie to be made, so more visits = higher denominator of volunteers + also higher chance at co-visits so unsure what to make
entropy_log_density <- lm(entropy ~ log_density, data =subset(sna_ego_list_for_model,density>0))
summary(entropy_log_density)
confint(entropy_log_density)

```
# Adjusted alter closeness shannon entropy models
```{r,adjusted_entropy} 
#### ADJUSTED MODELS ######
#entropy_models
entropy_age_adjusted <- lm(entropy ~ age + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of total admissions and los

summary(entropy_age_adjusted)
confint(entropy_age_adjusted)

#LOS and admissions
entropy_los_adjusted <- lm(entropy ~ log_total_los  + log_total_admissions, data =sna_ego_list_for_model)  
summary(entropy_los_adjusted)
confint(entropy_los_adjusted)


#deceased
entropy_deceased_adjusted <- lm(entropy ~ deceased + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(entropy_deceased_adjusted)
confint(entropy_deceased_adjusted)
#dpp
entropy_dpp_adjusted <- lm(entropy ~ dpp + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(entropy_dpp_adjusted)
confint(entropy_dpp_adjusted)

#project_team
entropy_project_team_adjusted <- lm(entropy ~ project_team + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(entropy_project_team_adjusted)
confint(entropy_project_team_adjusted)

#gender
entropy_gender_adjusted <- lm(entropy ~ gender + log_total_los + log_total_admissions, data =sna_ego_list_for_model)    #This model adds in the covariate effect of th
summary(entropy_gender_adjusted)
confint(entropy_gender_adjusted)
#log density
# This may be tied to the fact that each visit is a chance for a tie to be made, so more visits = higher denominator of volunteers + also higher chance at co-visits so unsure what to make
entropy_log_density_adjusted <- lm(entropy ~ log_density + log_total_los + log_total_admissions, data =subset(sna_ego_list_for_model,density>0))
summary(entropy_log_density_adjusted)
confint(entropy_log_density_adjusted)

```

Interpretation guide for betas
https://stats.idre.ucla.edu/other/mult-pkg/faq/general/faqhow-do-i-interpret-a-regression-model-when-some-variables-are-log-transformed/


# Table 1 


```{r, table1}

table1(~age + total_los+total_admissions+ dpp+ deceased+ gender+ network_size+ avg_alter_freq+ total_visits+ density+ entropy |project_team ,data=sna_ego_list_for_model)
```

